Hydra Battles and Cie

### 2021-08-22 doc/part-hydras.tex
conversion to Alectryon (chapter 5, more than half done)

\begin{Coqsrc}
Lemma LT_to_round_plus alpha beta :
    beta t1< alpha ->  iota alpha -+-> iota beta.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_path_to (alpha beta : T1) :
  beta t1< alpha -> {s : list nat | path_to beta s alpha}.
\end{Coqsrc}

The sequence $s$, used to build the sequence of replication factors of the battle depends on 
$\beta$, so we cannot be sure that the generated battle is a genuine standard battle.

@@

\begin{Coqsrc}
(**  standard path from (i, alpha) to (j, beta) *)

Inductive standard_pathR(j:nat)( beta:T1):  nat -> T1 -> Prop :=
  std_1 : forall i alpha, 
       beta = canon alpha i -> j = S i ->
       standard_pathR j beta i  alpha
| std_S : forall i alpha, 
      standard_pathR j beta (S i) (canon alpha i)  ->
      standard_pathR j beta i alpha.

Definition standard_path  i alpha j beta := 
   standard_pathR j beta i alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition const_pathS i :=
  clos_trans_1n T1 (fun alpha beta => alpha <> zero /\
                                      beta = canon alpha (S i)).

Definition const_path i alpha beta :=
  match i with
    0 => False
  | S j => const_pathS j alpha beta
end.
\end{Coqsrc}

>>>>

@@

The sequence $s$, used to build the sequence of replication factors of the battle, depends on 
$\beta$, so we cannot be sure that the generated battle is a genuine standard battle.

@@

\input{movies/snippets/Paths/standardPathR}

@@

\input{movies/snippets/Paths/constPathDef}
